### 2023-12-04 manuscript.tex
Added final results section on clusters

\subsection{Clustering by evolutionary signatures reveals limited patterns of conserved features}
We therefore fit OU models to the features calculated from the segments in each region to detect evidence of their conservation. A strength of probabilistic models of trait evolution is they permit the use of standard statistical methods to compare the support for different hypotheses. Thus, the goodness of fit of the OU model relative to that of the BM model is a measure of the evidence for selective constraint. However, because the OU model is specified with an additional parameter and has a greater capacity to fit the data, we compared their fits using the difference in the Akaike information criterion (AIC), which accounts for the model complexity, rather than the likelihood ratio. We chose not to treat these differences in a strict statistical sense but instead as qualitative ``evolutionary signatures'' as in Zarin \textit{et al.}~\cite{Zarin2019}. Accordingly, we clustered the signatures to identify patterns of feature conservation across the proteome.

% TODO: Re-write above paragraph to move directly into discussion of global properties of conserved features
% What is the distribution of number of ``conserved'' features across regions at a given cutoff?
% What fraction of IDRs has each feature conserved?
% Show some examples of IDRs with certain conserved features and plots of delta log-likelihoods with cutoffs indicated

The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise (Fig.~\ref{fig:hierarchy}). However, we identify at least 12 clusters with a strong and consistent patterns of constraint, with many having significant associations with certain processes, functions, or compartments. For example, cluster B is strongly enriched in proteins associated with the Wnt signaling pathway, and cluster F contains many proteins involved in nuclear transport. (Selected annotations corresponding to the summaries in Fig.~\ref{fig:hierarchy} are given in Table~\ref{stable:annotations}.) Though these preliminary results suggest the existence of a high-level relationship between certain patterns of conserved features and function, further insight into the mechanisms that underpin these associations will rely on more in-depth analyses of specific clusters and the properties of their constituent IDRs.

% TODO: Merge some of introduction from previous paragraph into this in order to introduce idea of investigating existence of global patterns of signatures
% Include some controls used in Zarin to ensure clustering is not based on sequence similarity
% Expand discussion of individual clusters, including specific conserved features and associated biological functions

>>>>

\subsection{Clustering by evolutionary signatures reveals limited patterns of conserved features}
Given our observation of widespread signals of feature conservation in \textit{Drosophila} IDRs, we next sought to investigate if there are IDRs with similar patterns of conserved features and common functions. Accordingly, we treated the set of likelihoods ratios for each region as its ``evolutionary signature'' and clustered them as in as in Zarin \textit{et al.}~\cite{Zarin2019}. The resulting heatmap reveals patterns of similar signatures interspersed among a high background of noise (Fig.~\ref{fig:hierarchy}). However, we identified at least 39 clusters with strong and consistent patterns of constraint. To gain greater insight into their functional properties, we performed term enrichment analyses on the sets of proteins with regions in each cluster. After correcting for multiple comparisons using a 5\% false discovery rate, only five clusters were significantly enriched for any terms, which are given in Table~\ref{table:cluster_terms}. Most enriched terms are associated with fewer than ten proteins in each cluster, though the enriched terms for cluster 12 are markedly stronger and consistently associated with protein localization. We also observed that while many clusters are defined by a single strongly conserved feature, three (clusters 15, 23, and 24) have multiple features with signals of constraint. To determine if these more highly constrained regions are associated with a common underlying pattern of features, we compared their evolutionary signatures to normalized values of their inferred optima (Fig.~\ref{fig:clusters}B-D). The heatmaps reveal that while the regions in these clusters have common patterns of constraint, the optimal values of their features can vary considerably. Likewise, cluster 12's strongly constrained feature, repeat\_K, is similarly variable (Fig.~\ref{fig:clusters}A). Interestingly, this feature is consistent with its enrichment in annotations related to protein localization, as mitochondrial or nuclear targeting signals are characterized by a net positive charge or clusters of basic residues, respectively~\cite{Moulin2019, Lu2021}. However, the relative depletion of lysine repeats in some regions implies they are constrained against the formation of targeting signals. This in turn suggests that IDRs may in general have complex relationships between their evolutionary constraints and functions where constraints can both preserve beneficial functions as well as prevent the acquisition of deleterious ones.
